---
title: "Gov 50 Final Project"
author: "Stephanie Iannaccone"
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
---

```{r}
library(tidyverse)
library(dplyr)
library(readr)
library(ggplot2)
```

```{r}
US_Daily_Climate_csv <- read_csv("~/Library/Mobile Documents/com~apple~Numbers/Documents/US_Daily_Climate_csv.csv")
View(US_Daily_Climate_csv)

US_Daily_Climate_csv$DATE <- as.Date(US_Daily_Climate_csv$DATE, format = "%Y-%m-%d")
```

```{r}
tempplot <- ggplot(data = US_Daily_Climate_csv, aes(x = `DLY-TMIN-NORMAL`, y = `DLY-TMAX-NORMAL`)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Relationship between Daily Minimum and Maximum Temperatures",
       x = "Daily Minimum Temperature",
       y = "Daily Maximum Temperature")
tempplot
```

```{r}
lineplot <- ggplot(data = US_Daily_Climate_csv, aes(x = DATE)) +
  geom_line(aes(y = `DLY-TMIN-NORMAL`, color = "Daily Min Temperature"), size = 1) +
  geom_line(aes(y = `DLY-TMAX-NORMAL`, color = "Daily Max Temperature"), size = 1) +
  labs(title = "Comparison of Daily Minimum and Maximum Temperatures",
       x = "Date",
       y = "Temperature") +
  scale_color_manual(values = c("Daily Min Temperature" = "blue", "Daily Max Temperature" = "red"))
lineplot
```


```{r}
summary_stats <- summarize(US_Daily_Climate_csv,
                            Mean_TMIN = mean(`DLY-TMIN-NORMAL`, na.rm = TRUE),
                            SD_TMIN = sd(`DLY-TMIN-NORMAL`, na.rm = TRUE),
                            Mean_TMAX = mean(`DLY-TMAX-NORMAL`, na.rm = TRUE),
                            SD_TMAX = sd(`DLY-TMAX-NORMAL`, na.rm = TRUE))

summary_stats

knitr::kable(summary_stats, digits = 2)

```
## Analysis Discussion

Daily Minimum Temperature:
Mean Daily Minimum Temperature: The calculated mean daily minimum temperature is 21.4째C. This statistic represents the average value of the daily minimum temperatures observed in the dataset. It serves as a central measure, indicating the typical temperature conditions for the given period.

Standard Deviation of Daily Minimum Temperature: The standard deviation of 282.04째C reflects the extent to which individual daily minimum temperatures deviate from the mean. A higher standard deviation suggests greater variability, indicating that the dataset may include days with widely different minimum temperatures.

Daily Maximum Temperature:
Mean Daily Maximum Temperature: The mean daily maximum temperature is 49.32째C, representing the average value of the daily maximum temperatures recorded. Similar to Mean_TMIN, this statistic provides a central measure for understanding typical temperature conditions.

Standard Deviation of Daily Maximum Temperature: With a standard deviation of 237.93째C, the variability in daily maximum temperatures is somewhat lower compared to the daily minimum temperatures. A lower standard deviation suggests that the maximum temperatures may exhibit less variability.

## Project thoughts
Stephanie Iannaccone
https://catalog.data.gov/dataset/u-s-daily-climate-normals-1981-20101

State your research question.

How have the daily climate normals for 1981 to 2010 in the United States evolved over time, and what are the regional variations and trends in maximum and minimum temperatures, precipitation, and wind patterns?

Formulate a hypothesis related to the research question. This hypothesis should be rooted in some sort of theory. In other words, you need to present a plausible story why the hypothesis might be true. Often, this is in the form of a behaviorial or institutional explanation. As social scientists, we are not interested in idiosyncratic explanations; we want to understand systematic patterns and relationships!

Hypothesis:Based on the U.S. Daily Climate Normals dataset for 1981 to 2010, I hypothesize that there has been a statistically significant increase in the average maximum temperatures across the United States during this 30-year period. This increase is likely due to climate change and can be shown by analyzing the daily maximum temperature normals at a regional scale.

Describe your explanatory variable(s) of interest and how it is measured. Importantly, we need to observe variation in this variable in order to study it!

Explanatory Variable: The explanatory variables are geographic location and is defined by latitude and longitude. Time is analyze how climate normals have changed over this specific time frame through the meteorological parameters. Elevation of the weather station location can help when studying how temperature and other meteorological parameters are influenced by altitude. 

Geographic location is measured by latitude and longitude coordinates. Time is measured in years or months within the specified 30-year period. Elevation is measured in feet above sea level. 

Describe your outcome variable of interest and how it is measured.

Outcome Variable: The outcome variable of interest is the daily maximum temperature normal. This variable represents the long-term average daily maximum temperature for specific locations across the United States and other included regions over the 30-year period from 1981 to 2010. The daily maximum temperature normal is measured in degrees Fahrenheit and is derived from historical meteorological data collected at thousands of weather stations, including those in the NWS Cooperative Observer Program (COOP) Network, Weather Bureau Army-Navy (WBAN) stations, and stations from the Climate Reference Network (CRN).

Observed Pattern Supporting Hypothesis: An observed pattern supporting the hypothesis that there has been a statistically significant increase in the average maximum temperatures across the United States during the 30-year period from 1981 to 2010.

Observed Pattern Disproving Hypothesis: The observed pattern shows that there was no statistically significant increase in the average maximum temperatures or even a decrease over the 30-year period.

Data Section: The dataset consists of weather records for the station includes information such as elevation, latitude, longitude, date, and various temperature and precipitation metrics. The relevant variables for analysis include DATE, DLY-TMIN-NORMAL which is daily minimum temperature, DLY-TMAX-NORMAL which is daily maximum temperature, and MTD-PRCP-NORMAL which is month-to-date precipitation. The main objective of the U.S. Daily Climate Normals dataset analysis from 1981 to 2010 was to look into regional variations in maximum temperature changes. Figuring out if there has been a noticeable rise in maximum temperatures that could be linked to climate change was the main goal. The study used regression analysis and exploratory data analysis with time, location, and elevation taken into account as explanatory variables in order to do this. The results showed a statistically significant rising trend in average maximum temperatures, indicating a notable change in the patterns of the climate over the given time period. The study offers insightful information on how temperature trends are affected by climate change, and it highlights the need for more investigation to fully understand the complexity of the patterns seen and the possible causes of them.


Conclusion: In conclusion, the study of the U.S. Daily climate Normals dataset spanning from 1981 to 2010 provided insightful information about how the country's climate trends have changed over time. With a focus on maximum temperatures, the research investigated regional differences and patterns under the assumption that there would be a notable rise associated with climate change. The project aimed to represent the complex structure of climate patterns by taking elevation, time, and geographic location into account as explanatory variables. Both exploratory data analysis and regression analysis were performed on the dataset, which included meteorological data from multiple weather stations. The findings, which show a statistically significant rising trend in average maximum temperatures, advance our knowledge of the development of the climate while underscoring the significance of cautious interpretation and taking potential confounders into account. These discoveries increase our understanding of climate change.