---
title: "Gov 50 Final Project"
author: "Stephanie Iannaccone"
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
---

```{r}
library(tidyverse)
library(dplyr)
library(readr)
library(ggplot2)
```

```{r}
US_Daily_Climate_csv <- read_csv("~/Library/Mobile Documents/com~apple~Numbers/Documents/US_Daily_Climate_csv.csv")
View(US_Daily_Climate_csv)
```

```{r}
US_Daily_Climate <- ggplot(data = US_Daily_Climate_csv, 
       mapping = aes(x = `MTD-PRCP-NORMAL`)) +
  geom_bar()
US_Daily_Climate
```



## Project thoughts
Stephanie Iannaccone
https://catalog.data.gov/dataset/u-s-daily-climate-normals-1981-20101

State your research question.

How have the daily climate normals for 1981 to 2010 in the United States evolved over time, and what are the regional variations and trends in maximum and minimum temperatures, precipitation, and wind patterns?

Formulate a hypothesis related to the research question. This hypothesis should be rooted in some sort of theory. In other words, you need to present a plausible story why the hypothesis might be true. Often, this is in the form of a behaviorial or institutional explanation. As social scientists, we are not interested in idiosyncratic explanations; we want to understand systematic patterns and relationships!

Hypothesis:Based on the U.S. Daily Climate Normals dataset for 1981 to 2010, I hypothesize that there has been a statistically significant increase in the average maximum temperatures across the United States during this 30-year period. This increase is likely due to climate change and can be shown by analyzing the daily maximum temperature normals at a regional scale.

Describe your explanatory variable(s) of interest and how it is measured. Importantly, we need to observe variation in this variable in order to study it!

Explanatory Variable: The explanatory variables are geographic location and is defined by latitude and longitude. Time is analyze how climate normals have changed over this specific time frame through the meteorological parameters. Elevation of the weather station location can help when studying how temperature and other meteorological parameters are influenced by altitude. 

Geographic location is measured by latitude and longitude coordinates. Time is measured in years or months within the specified 30-year period. Elevation is measured in feet above sea level. 

Describe your outcome variable of interest and how it is measured.

Outcome Variable: The outcome variable of interest is the daily maximum temperature normal. This variable represents the long-term average daily maximum temperature for specific locations across the United States and other included regions over the 30-year period from 1981 to 2010. The daily maximum temperature normal is measured in degrees Fahrenheit and is derived from historical meteorological data collected at thousands of weather stations, including those in the NWS Cooperative Observer Program (COOP) Network, Weather Bureau Army-Navy (WBAN) stations, and stations from the Climate Reference Network (CRN).

Observed Pattern Supporting Hypothesis: An observed pattern supporting the hypothesis that there has been a statistically significant increase in the average maximum temperatures across the United States during the 30-year period from 1981 to 2010.

Observed Pattern Disproving Hypothesis: The observed pattern shows that there was no statistically significant increase in the average maximum temperatures or even a decrease over the 30-year period.